---
title: Juggling with S7
author: Ella Kaye
date: 2026-06-09
date-format: long
execute:
  echo: true
  eval: true
format: 
  revealjs: 
    theme: jugglr.scss
    syntax-highlighting: jugglr.theme
    width: 1280
    height: 720
filters:
  - diagrams
---

## {background-image="images/learning.png" background-size="contain"}

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(message = TRUE)
```

## {background-image="images/juggling.png" background-size="contain"}

## {background-image="images/maths.png" background-size="contain"}

## {background-image="images/packages.png" background-size="contain"}

## {background-image="images/jugglr-interest.png" background-size="contain"}

# siteswap {.inverse .center-h .larger200}

## {background-image="images/3.gif" background-size="33%" background-position="50% 80%"}

## [33333...]{.larger250 .dark} {background-image="images/3.gif" background-size="33%" background-position="50% 80%"}

## [3]{.larger250 .dark} {background-image="images/3.gif" background-size="33%" background-position="50% 80%"}

## [4]{.larger250 .dark} {background-image="images/4-cols.gif" background-size="33%" background-position="50% 80%"}

## [423]{.larger250 .dark} {background-image="images/423.gif" background-size="33%" background-position="50% 80%"}

## [(4,4)]{.larger250 .dark} {background-image="images/4s.gif" background-size="33%" background-position="50% 80%"}

## [(4x,4x)]{.larger250 .dark} {background-image="images/4x4x.gif" background-size="33%" background-position="50% 80%"}

## [[43]14]{.larger250 .dark} {background-image="images/4314.gif" background-size="33%" background-position="50% 80%"}

## [(2,6x)([6x4x],2x)]{.larger250 .dark} {background-image="images/sync_multi.gif" background-size="33%" background-position="50% 80%"}

## [<3p|3p>]{.larger250 .dark} {background-image="images/3p.gif" background-size="33%" background-position="50% 80%"}

# {background-image="images/jugglr.png" background-size="contain"}

## Create and validate (juggleable) siteswap

```{r}
library(jugglr)
ss423 <- siteswap("423")
ss423
```

## Create and validate (unjuggleable) siteswap

```{r}
ss432 <- siteswap("432")
ss432
```

## Visualise with `timeline`

```{r}
timeline(ss423)
```

## Visualise with `timeline`

```{r}
timeline(ss432)
```

## Visualise with `ladder`

```{r}
ladder(ss423)
```

## Visualise with `ladder`

```{r}
ladder(ss432)
```

# S7 {.inverse .center-h .larger200}

# Slide templates {.inverse}

## Colours

Colour classes for text and highlights:

:::: {.columns}
::: {.column}
[neon-green]{.neon-green}

[neon-blue]{.neon-blue}

[neon-pink]{.neon-pink}

:::


::: {.column}
[neon-green-hl]{.neon-green-hl}

[neon-blue-hl]{.neon-blue-hl}

[neon-pink-hl]{.neon-pink-hl}

[neon-coral-hl]{.neon-coral-hl}

[neon-orange-hl]{.neon-orange-hl}

[neon-yellow-hl]{.neon-yellow-hl}
:::
::::

## Colours inverse {.inverse}

Colour classes for text and highlights:

:::: {.columns}
::: {.column}

[pastel-purple]{.pastel-purple}

[pastel-pink]{.pastel-pink}

[pastel-green]{.pastel-green}

[pastel-blue]{.pastel-blue}
:::


::: {.column}
[pastel-pink-hl]{.pastel-pink-hl}

[pastel-green-hl]{.pastel-green-hl}

[pastel-blue-hl]{.pastel-blue-hl}

[pastel-purple-hl]{.pastel-purple-hl}
:::
::::


## Columns with backgrounds

Use class `.col-box-{color}` to apply colour box styling

::: {columns}
::: {.column .col-box-neon-pink width="32%"}
Box 1: pink

Default height is 450px
:::

::: {.column .col-box-neon-blue width="32%"}
Box 2: blue

:::

::: {.column .col-box-neon-green width="32%"}
Box 3: green
:::
:::

## Columns with backgrounds

::::: {columns}
:::: {.column .col-box-pastel-green-tall width="49%"}
Colour box styling can be applied to entire columns

This has height 600px
::::

:::: {.column width="49%"}
:::{.col-box-pastel-pink-short}
Or to divs within columns to create stacks
:::

:::{.col-box-pastel-blue-short}
This div has height 300px
:::

::::

:::::

## Custom callouts {.smaller80}

:::{.callout-note}
A note
:::

:::{.callout-warning}
A warning
:::

:::{.callout-important}
Something important
:::

:::{.callout-tip}
This is a good idea
:::

:::{.callout-caution}
Be careful about doing this
:::

## Syntax highlighting

```{r}
#| echo: true
#| eval: false
library(dplyr)

penguins %>%
  mutate(
    long_flipper = case_when(
      species == "Adelie" & flipper_len > 195 ~ TRUE,
      species == "Chinstrap" & flipper_len > 200 ~ TRUE,
      species == "Gentoo" & flipper_len > 225 ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  mutate(
    body_mass_kg = body_mass / 1000,
    bill_len_cm = bill_len / 10,
    bill_dep_cm = bill_dep / 10
  )
```